Predicting sales of newly published books

### 2015-10-16 paper.tex
working in the results section

Trevenque company, whose expert manager advised this research,
provided %FERGU: los párrafos anteriores son un poco dispersos, puedes
         %quitar los puntos y aparte y agruparlos por temas (por
         %ejemplo, todo lo de Trevenque debería de ir en un párrafo) 
% O borrarlos - JJ
%% Fin de párrafos a eliminar.
This initial data set, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information for each book includes price, 
points of sale, subject, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

\begin{minipage}{2.3in} \begin{verbatim}
REFERENCE
AUTHOR
RETAIL PRICER
SUBJECT1
SUBJECT2
SUBJECT3
EDITORIAL
COLLECTION
BOOKBINDING
PRINT-RUN
TOTAL SALES
DEPARTMENT STORES SALES
SALES THROUGH DELEGATES
REST OF SALES
TOTAL SALES FIRST YEAR
MALL SALES FIRST YEAR
DELEGATES SALES FIRST YEAR
REST OF SALES FIRST YEAR
TOTAL DISTRIBUTED
DISTRIBUTED THROUGH DEPARTMENT STORES
DISTRIBUTED THROUGH DELEGATES
DISTRIBUTED - REST
TOTAL DISTRIBUTED FIRST YEAR
DISTRIBUTED THROUGH DEPARTMENT STORES FIRST YEAR
DISTRIBUTED THROUGH DELEGATES FIRST YEAR
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
REST OF DISTRIBUTED FIRST YEAR
REPRINTS
NUMBER OF REPRINTS
TOTAL RETURNS
RETURNS - DEPARTMENT STORES
DELEGATES RETURNS
REST OF RETURNS
TOTAL RETURNS FIRT YEAR
RETURNS -  DEPARTMENT STORES  FIRST YEAR
DELEGATES RETURNS FIRST YEAR
REST OF RETURNS FIRST YEAR
GIFTS
UNITS DISTRIBUTED AS NOVELTY
TOTAL POINTS OF SALE
POINTS OF SALE - DEPARTMENT STORES
DELEGATES POINTS OF SALE
REST OF POINTS OF SALE
TOTAL POINTS OF SALE FIRST YEAR
DEPARTMENT STORES POINTS OF SALE FIRST YEAR
DELEGATES POINTS OF SALE FIRST YEAR
REST OF POINTS OF SALE FIRST YEAR
WEEKS FOR SALE
POSITIVE SALES ENVIRONMENT
MEDIUM SALES ENVIRONMENT
NEGATIVE SALES ENVIRONMENT
\end{verbatim} \end{minipage}    \\

@@

%
% TODO: explicar los resultados obtenidos en la selección de variables: 
%  (1) con el SOM, (2) con los métodos de selecc. vars.
%
% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
To do so, in a first stage, the feature selection process has been carried out 
using both the CfsSubsetEval \cite{Hall1998} (a correlation-based feature subset 
evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
adaptation of relief for attribute estimation) evaluation methods.

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print_run, num_reprints, tot_points_sale, tot_points_sale_1st_year, reprints, distrib_novelty, weeks_sale, total_sales}.

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the CfsSubsetEval feature selection method, the following variables have 
been selected: \emph{num_reprints, tot_points_sale, print_run, total_sales}.

@@

\textbf{ TODO: add the SOM analisys }

Once the different reduced datasets have been obtained, proposed methods 
(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialization seed for each run.

@@

>>>>

Trevenque company, whose expert manager advised this research,
provided %FERGU: los párrafos anteriores son un poco dispersos, puedes
         %quitar los puntos y aparte y agruparlos por temas (por
         %ejemplo, todo lo de Trevenque debería de ir en un párrafo) 
% O borrarlos - JJ
%% Fin de párrafos a eliminar.
This initial data set, provided in the framework of a contract by
Trevenque Editorial, included 3159 books, and included descriptive information 
for each book, such as price, points of sale, subject, publisher, sales, returns, 
among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

\begin{minipage}{2.3in} \begin{verbatim}
reference
author
retail pricer
subject1
subject2
subject3
editorial
collection
bookbinding
print-run
total sales
department stores sales
sales through delegates
rest of sales
total sales first year
mall sales first year
delegates sales first year
rest of sales first year
total distributed
distributed through department stores
distributed through delegates
distributed - rest
total distributed first year
distributed through department stores first year
distributed through delegates first year
\end{verbatim} \end{minipage}     &

\begin{minipage}{2.3in} \begin{verbatim}
rest of distributed first year
reprints
number of reprints
total returns
returns - department stores
delegates returns
rest of returns
total returns firt year
returns -  department stores  first year
delegates returns first year
rest of returns first year
gifts
units distributed as novelty
total points of sale
points of sale - department stores
delegates points of sale
rest of points of sale
total points of sale first year
department stores points of sale first year
delegates points of sale first year
rest of points of sale first year
weeks for sale
positive sales environment
medium sales environment
negative sales environment
\end{verbatim} \end{minipage}    \\

@@

%
% TODO: explicar los resultados obtenidos en la selección de variables: 
%  (1) con el SOM, (2) con los métodos de selecc. vars.
%
% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
To do so, in a first stage, the feature selection process has been carried out 
using both the CfsSubsetEval \cite{Hall1998} (a correlation-based feature subset 
evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
adaptation of relief for attribute estimation) evaluation methods, implemented 
in the Weka tool.

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked atributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the CfsSubsetEval feature selection method, the following variables have 
been selected: \emph{number of reprints, total points of sale, print-run, total sales}.

@@

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
% Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analisys }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

Once the different reduced datasets have been obtained, proposed methods 
(M5P, LR, SVM, kNN, MLP) have been selected for this study from 
the Weka implementation, and they were run 30 times with the Weka default parameter 
settings and a different random initialization seed for each run and each dataset.

@@

% datasets:
%  original (all vars)
%  4 vars
%  9 vars
%  SOM selected vars
